Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-10-25 Paper.tex
Add security & quality considerations

During development and in order to ease
the automatic deployment of the contract
over a Truffle's suite Ganache-CLI\ref{ganache}
instance there are two util scripts on the
repository\cite{state-channel-contract-a}
\texttt{utils/compile.js} and \texttt{utils/deploy.js}
that take care of merging all the Solidity source
code required and deploying it to the Ganache instance.

@@

In repository\cite{state-channel-contract-a} module
\texttt{tests/main.test.js} there are the following Mocha
framework\cite{mocha} based tests; tests use Chai assertion
library\cite{chai} using its \textit{should} mode whenever
possible but some of the assertions still have to be done
by \texttt{try-catch} pattern due to Chai not supporting
at the time of writing \texttt{BigInt} operation.

@@

>>>>

During development and in order to ease
the automatic deployment of the contract
over a Truffle's suite Ganache-CLI\cite{ganache}
instance there are two util scripts on the
repository\cite{state-channel-contract-a}
\texttt{utils/compile.js} and \texttt{utils/deploy.js}
that take care of merging all the Solidity source
code required and deploying it to the Ganache instance.

@@

In repository\cite{state-channel-contract-a} module
\texttt{main.test.js} there are the following Mocha
framework\cite{mocha} based tests; tests use Chai assertion
library\cite{chai} using its \textit{should} mode whenever
possible but some of the assertions still have to be done
by \texttt{try-catch} pattern due to Chai not supporting
at the time of writing \texttt{BigInt} operation.

Non-trivial tests covering main workflows include:
\begin{itemize}
\item Contract requires a minimum value amount to open a channel.
\item A user can open a channel sending value over a minimum amount sending
  also an Ethereum ephemeral public key
\item Prevention of closing channel operation using a different private key
  in signature.
\item Ability of the contract owner to close the channel using a properly
  generated user signature.
\item If channel is not closed by the owner, the user, cannot close it
  before a certain amount of time.
\item In case reaching expiration time without the owner properly closing the channel,
  the user can close the channel receiving in return unexpended amount.
\end{itemize}

\subsection{Front-end \& Back-end manual testing}

Both components were heavily manually tested, during development
in order to assure the correct workflows were correctly supported.

@@

\section{Security considerations}

\subsection{Network security}

Network security of the PoC depicted in this work
has some issues having to do with the ability of
an attacker to associate to owner's network without
any authentication nor authorization protocol; taking
this into account, special care has to be taken to
properly secure any attack surface:

\begin{itemize}
\item Add firewall rules to prevent IP traffic between
  different end users.
\item Obviously securize the connectivity to the Raspberry
  using a wire connection and filtering any traffic on 22 (ssh)
  port coming from the wireless interface.
\item For this PoC, using only the captive portal IP address; TLS
  is not supported; accordingly the user has no guarantee of
  authenticity of the WiFi service provider.
\end{itemize}

\subsection{Cryptographic security}

All smart contract-blockchain transactions are being processed
using Infura as an Ethereum proxy; only security issue regarding
private key management arises when considering the ephemeral
private keypair generation on the front-end.

\subsection{Security summary}
